---
title: "Accordion Plays"
author: "Jack Penzer"
date: "2023-07-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(bslib)
library(shiny)
```


For the WLOs tab, create a tab which has an accordion for the whole thing. Then inside the accordion the first panel is the text, the second is the sidebar_layout with the plotting controls which is an accordion

```{r}
ui <-  
  bslib::page_fillable(
    # card(
    accordion(
      id = "accordion",
      accordion_panel(
        id = "item1",
        title = "text",
        bigram_text()
      ),
      accordion_panel(
        title = "Sidebar",
        id = "accordionsidebar",
        layout_sidebar(
          fillable = TRUE,
          fill = TRUE,
          sidebar = sidebar(
            id = "sidebar1",
            shiny::sliderInput("height", "height", min = 100, max = 1200, value = 600, step = 50),
            shiny::sliderInput("width", "width", min = 100, max = 1200, value = 800, step = 50)
          ),
          #some stuff
          textAreaInput(
            inputId = "text1",
            label = "text input"
          )
        )
      )
      
    )
    # )
  )


server <-function(input, output, session){
  
}

shinyApp(ui, server)

```


```{r}
tagList(
    bslib::page_fillable(
      bslib::accordion(
        id = ns("accordion"),
        bslib::accordion_panel(
          id = ns("item1"),
          title = "Weighted log-odds",
          active = TRUE,
          bslib::accordion_panel(
            id = ns("wlosText"),
            title = "",
            active = TRUE,
            wlos_text()
          ),
          bslib::layout_sidebar(
            fill = TRUE,
            bslib::sidebar(bg = "white",
                           bslib::accordion(
                             id = ns("accordion2"),
                             bslib::accordion_panel(
                               id = ns("item2"),
                               title = "Aesthetic Controls",
                               active = FALSE,
                               shiny::sliderInput(inputId = ns("height"), "height", min = 100, max = 1400, value = 800, step = 100),
                               shiny::sliderInput(inputId = ns("width"), "width", min = 100, max = 1200, value = 600, step = 100),
                               shiny::sliderInput(inputId = ns("textSize"), "text size", min = 2, max = 8, value = 4, step = 1),
                               shiny::sliderInput(inputId = ns("nrow"), label = "number of rows", min = 1, max = 20, value = 10, step = 1),
                             ),
                             bslib::accordion_panel(
                               id = ns("item3"),
                               title = "Parameters",
                               active = TRUE,
                               shiny::sliderInput(
                                 inputId = ns("topN"),
                                 label = "top_n",
                                 min = 15,
                                 max = 60,
                                 value = 30,
                                 step = 5
                               ),
                               shiny::sliderInput(
                                 inputId = ns("termCutoff"),
                                 label = "top terms cutoff",
                                 min = 500,
                                 max = 5000, value = 2500,
                                 step = 100
                               ),
                               shiny::selectInput(
                                 inputId = ns("groupVar"),
                                 label = "select your grouping variable",
                                 choices = NULL
                               ),
                               shiny::downloadButton(outputId = ns("saveWLOs"), class = "btn btn-warning")
                             ),
                           ),
            ),
            bslib::accordion(
              id = ns("accordion3"),
              bslib::accordion_panel(
                id = ns("item3"),
                title = "WLOs plot",
                active = FALSE,
                shinycssloaders::withSpinner(shiny::plotOutput(ns("wlosPlot"),
                                                               height = "800px",
                                                               width = "600px")
                )
              )
            )
          )
        ),
      ),

  )
)
```


card with layout inside with accordions inside, which sits inside cards and accordions
```{r}
bslib::card(full_screen = TRUE,
                      bslib::layout_sidebar(
                        fill = TRUE,
                        bslib::sidebar(bg = "white",
                                       bslib::accordion(
                                         id = ns("nestedAccordion1"),
                                         bslib::accordion_panel(

                                           id = ns("nested1item1"),
                                           title = "Aesthetic Controls",
                                           active = FALSE,
                                           icon = shiny::icon(name = "wand-magic-sparkles"),
                                           shiny::sliderInput(inputId = ns("height"), "height", min = 100, max = 1400, value = 800, step = 100),
                                           shiny::sliderInput(inputId = ns("width"), "width", min = 100, max = 1200, value = 600, step = 100),
                                           shiny::sliderInput(inputId = ns("textSize"), "text size", min = 2, max = 8, value = 4, step = 1),
                                           shiny::sliderInput(inputId = ns("nrow"), label = "number of rows", min = 1, max = 20, value = 10, step = 1),
                                         ),
                                         bslib::accordion_panel(
                                           id = ns("nested1item2"),
                                           title = "Parameters",
                                           active = TRUE,
                                           icon = shiny::icon("wrench"),
                                           shiny::sliderInput(
                                             inputId = ns("topN"),
                                             label = "top_n",
                                             min = 15,
                                             max = 60,
                                             value = 30,
                                             step = 5
                                           ),
                                           shiny::sliderInput(
                                             inputId = ns("termCutoff"),
                                             label = "top terms cutoff",
                                             min = 500,
                                             max = 5000, value = 2500,
                                             step = 100
                                           ),
                                           shiny::selectInput(
                                             inputId = ns("groupVar"),
                                             label = "select your grouping variable",
                                             choices = NULL
                                           ),
                                           shiny::downloadButton(outputId = ns("saveWLOs"), class = "btn btn-warning")
                                         ),
                                       ),
                        ),
                        bslib::accordion(
                          id = ns("nestedAccordion2"),
                          bslib::accordion_panel(
                            id = ns("nested2item1"),
                            title = "WLOs plot",
                            active = FALSE,
                            icon = shiny::icon("cloud-word"),
                            # bslib::card( full_screen = TRUE,
                            shinycssloaders::withSpinner(
                              shiny::plotOutput(
                                ns("wlosPlot"),
                                height = "800px",
                                width = "600px"
                              )
                            )
                            # ) #blisb::card
                          )
                        )
                      )
                      )
```

Nested accordions with cards inside
```{r}
tagList(
    bslib::page_fillable(
      bslib::accordion(
        id = ns("mainAccordion"),
        bslib::accordion_panel(
          id = ns("item1"),
          title = "Weighted Log-odds",
          active = TRUE,
          bslib::accordion_panel(
            id = ns("wlosText"),
            title = "Settings & Inputs",
            active = TRUE,
            wlos_text() #saved in zzz.R
          ),
          bslib::card(
            full_screen = TRUE,
            bslib::layout_sidebar(
              fill = TRUE,
              bslib::sidebar(
                bg = "white",
                bslib::accordion(
                  open = "nested1item2",
                  id = ns("nestedAccordion1"),
                  bslib::accordion_panel(
                    id = ns("nested1item1"),
                    title = "Aesthetic Controls",
                    open = "closed",
                    icon = shiny::icon("wand-magic-sparkles"),
                    shiny::sliderInput(
                      inputId = ns("height"), "height", min = 100, max = 1400, value = 800, step = 100),
                    shiny::sliderInput(inputId = ns("width"), "width", min = 100, max = 1200, value = 600, step = 100),
                    shiny::sliderInput(inputId = ns("textSize"), "text size", min = 2, max = 8, value = 4, step = 1),
                    shiny::sliderInput(inputId = ns("nrow"), label = "number of rows", min = 1, max = 20, value = 10, step = 1),
                  ),
                  bslib::accordion_panel(
                    id = ns("nested1item2"),
                    title = "Parameters",
                    open = TRUE,
                    icon = shiny::icon("wrench"),
                    shiny::sliderInput(
                      inputId = ns("topN"),
                      label = "top_n",
                      min = 15,
                      max = 60,
                      value = 30,
                      step = 5
                    ),
                    shiny::sliderInput(
                      inputId = ns("termCutoff"),
                      label = "top terms cutoff",
                      min = 30,
                      max = 5000,
                      value = 500,
                      step = 100
                    ),
                    shiny::downloadButton(outputId = ns("saveWLOs"), class = "btn btn-warning")
                  ),
                ),
              ),
              bslib::accordion(
                id = ns("nestedAccordion2"),
                bslib::accordion_panel(
                  id = ns("nested2item1"),
                  title = "WLOs plot",
                  active = FALSE,
                  icon = shiny::icon("cloud-word"),
                  shinycssloaders::withSpinner(
                    shiny::plotOutput(
                      ns("wlosPlot"),
                      height = "800px",
                      width = "600px"
                    )
                  )
                )
              )
            )
          )
        ),
      ),
    )
  )
```

card -> WLOS text in its own accordion, followed by the settings & WLO plot in another accordion with a sidebar
```{r}
ui <- bslib::page_fillable(
  bslib::card(
    full_screen = TRUE,
    bslib::accordion(#WLOs text
      id = "wlosText",
      bslib::accordion_panel(
        value = "wlosTextAccordion",
        title = "Settings & Inputs",
        wlos_text()
      )
    ), # settings + Plot
    bslib::layout_sidebar(
      bslib::sidebar(
        bslib::accordion(
          id = "inputs",
          bslib::accordion_panel(
            title = "Aesthetics",
          ),
          bslib::accordion_panel(
            title = "Parameters"
          )
        )
      ),
      shiny::textAreaInput(inputId = "wlosplot", label = "WLOSPLOT")
    )
  )
)


server <- function(input, output, session) {
  
}

shinyApp(ui, server)
```


Group plots/tab

Each plot is already an accordion in the overall module. But we want a card for the full screen and collapsible sub-menus
